### 2017-06-24 src/4_OnlineLearning.tex
background 2016  include finished
Background revision 2015 2016 elsevier ready

In order to avoid the singularity of the matrix $\mathbf{A}^\top \mathbf{A}$, a regularisation term is introduced:

@@

%REVISADO HASTA ACA

@@

Equation~(\ref{eq:optsolRR}) can also be written as:
\begin{eqnarray*}
\label{eq:RReapand}
\mathbf{\mathbf{X}}_{\text{ridge}}&=&(\mathbf{A}^\top \mathbf{A}+ \lambda
\mathbb{I})^{-1}\mathbf{A}^\top \mathbf{Y} \\
&=& \displaystyle \big (\sum_{t=1}^m
\mathbf{a}_t \mathbf{a}_t  ^\top + \lambda \mathbb{I}\big )^{-1}
\sum_{t=1}^m \mathbf{a}_t \mathbf{y}_t \, .
\end{eqnarray*}

>>>>

In order to avoid the singularity of the matrix $\mathbf{A}^\top \mathbf{A}$, a regularisation term $\lambda$ is introduced:

@@

@@

\noindent equation~(\ref{eq:optsolRR}) can also be written as:

\begin{eqnarray*}
\label{eq:RReapand}
\mathbf{\mathbf{X}}_{\text{ridge}}&=&(\mathbf{A}^\top \mathbf{A}+ \lambda
\mathbb{I})^{-1}\mathbf{A}^\top \mathbf{Y} \\
&=& \displaystyle \big (\sum_{t=1}^m
\mathbf{a}_t \mathbf{a}_t  ^\top + \lambda \mathbb{I}\big )^{-1}
\sum_{t=1}^m \mathbf{a}_t \mathbf{y}_t \, .
\end{eqnarray*}
